Make any stupid plot you want

### 2021-05-10 draft/sections/math.tex
data section

\section{Topological Equivariant Artist Model}
\label{sec:math}
To guide the implementation of structure preserving visualization components, we develop a mathematical formalism of visualization that specifies how these components preserve \textit{continuity} and \textit{equivariance}. Inspired by the analogous classes in Matplotlib\cite{hunterArchitectureOpenSource}, we call the transformation from data space to graphic space that these building block components implement the \textit{artist}.
\begin{equation}
    \label{eq:artist}
    \mathscr{\vartist}: \mathscr{\dtotal} \rightarrow \mathscr{\gtotal}
\end{equation}
The \textit{artist} $\mathscr{\vartist}$ is a map from data $\mathscr{\dtotal}$ to graphic $\mathscr{\gtotal}$ fiber bundles. To explain how the \textit{artist} is a structure preserving map from data to graphic, we first model data (\autoref{sec:math:data}) and graphics (\autoref{sec:math:graphic}) as topological structures that encapsulate component types and continuity. We then discuss the functional maps from graphic to data (\autoref{sec:math:graphic:base}), data components to visual components (\autoref{sec:math:artist:nu}), and visual components into graphic (\autoref{sec:math:artist:q}) that make up the artist.

\subsection{Data Space \dtotal}
\label{sec:math:data}
We use fiber bundles as the data model because they are inclusive enough to express all the types of structures of data described in \autoref{sec:intro:data:tools}. A fiber bundle is a tuple $(\dtotal,\,\dbase,\,\pi ,\,\dfiber)$ defined by the projection map $\pi$
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[r, "\pi"] & \dbase
    \end{tikzcd}
\end{equation}
that binds the components of the data in \dfiber\ to the continuity of the data encoded in \dbase. Our use of fiber bundles builds on Butler's work proposing that fiber bundles should be the common data abstraction for visualization data\cite{butlerVectorBundleClassesForm1992, butlerVisualizationModelBased1989}. The fiber bundle models the properties of data component types \dfiber\ (\autoref{sec:math:data:fiber}), the continuity of records \dbase\ (\autoref{sec:math:data:base}), the collections of records (\autoref{sec:math:data:section}), and the space \dtotal\ of all possible datasets with these components and continuity. By definition fiber bundles are locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}, meaning that over a localized neighborhood $U$ the total space is the cartesian product $\dbase\times\dfiber$.

\subsubsection{Variables in Fiber Space \dfiber}
\label{sec:math:data:fiber}
To formalize the structure of the data components, we use Spivak's description of the schema \cite{spivakSIMPLICIALDATABASES} as a fiber bundle to bind the components of the fiber to variable names and data types. Spivak constructs a set \ftotal\ that is the disjoint union of all possible objects of types $\{\ftype_0, \ldots, \ftype_m\} \in \ftypes$, where \ftypes\ are the data types of the variables in the dataset. He then defines the single variable set \fttype\ 
\begin{equation}
    \label{eq:data_types}
    \begin{tikzcd}
        \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] & \ftotal \arrow[d, "\pi"] \\
        \fnames \arrow[r, "\fsection"']                          & \ftypes       
    \end{tikzcd}
\end{equation}
which is \ftotal\ restricted to objects of type \ftype\ bound to variable name \fname. The \fttype\ lookup is by name to specify that every component is distinct, since multiple components can have the same type \ftype. Given \fsection, the fiber for a one variable dataset is
\begin{equation}
    \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
\end{equation}
where \fsection\ is the schema that binds a variable name \fname\ to its datatype \ftype. A dataset with multiple components has a fiber that is the cartesian cross product of $\ftotal_{\fsection}$ applied to all the columns:
\begin{equation}
F = \ftotal_{\fsection(\fname_{1})}\times \ldots \ftotal_{\fsection(\fname_{i})} \ldots\times \ftotal_{\fsection(\fname_{n})}
\end{equation}
which can also be written as 
\begin{equation}
    \label{eq:math:data:fiber:decompose}
    \dfiber= \dfiber_{0} \times \ldots \times \dfiber_{i}\times\ldots\times \dfiber_{n}
\end{equation}
which allows us to decouple \dfiber\ into components $\dfiber_i = \ftotal_{\fsection{(\fname_{i})}}$.

@@

The base space \dbase\ provides a way to explicitly encode the continuity of the data, as described in \autoref{sec:intro:data:continuity}. This explicit topology is a concise way of distinguishing between visualizations that appear identical but assume different continuity, for example heat maps and images. The base space \dbase\ acts as an indexing space, as emphasized by Butler\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, to express how the records in \dtotal\ are connected to each other. As shown in \autoref{fig:math:data:base:types}, \dbase\ can have any number of dimensions and can be continuous or discrete. Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every $\dbasepoint \in \dbase$ has a corresponding fiber $\dfiber_k$\cite{QuotientSpaceTopology2020}.

\begin{figure}[H]
    \includegraphics[width=\linewidth]{figures/math/k_qspace.png}
    \caption{The total space \dtotal\ is divided into fiber segments \dfiber. The base space \dbase\ acts as an index into the records in the fibers, such that every point \dbasepoint\ has a corresponding fiber $\dfiber_{\dbasepoint}$. The projection map $\pi$ maps every fiber $\dfiber_{\dbasepoint}$ to a point $\dbasepoint \in \dbase$ in the base space.}
    \label{fig:math:data:base:div}
\end{figure}

In \autoref{fig:math:data:base:div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping $\pi: \dtotal\rightarrow \dbase$ is the closed interval $\left[0,1\right]$. While the total space \dtotal\ may have components in \dfiber\ that describe any given point $\dbasepoint \in \dbase$, such as \textit{time, latitude, longitude}, these labels are indexed into from \dbase\ the same as any other components. In contrast to the structural \textit{keys} with associated \textit{values} proposed by Munzner\cite{munznerVisualizationAnalysisDesign2014}, our model treats keys \dbasepoint\ as a pure reference to topology. Decoupling the keys from their semantics allows the components identifying the keys to be altered, which provides for coordinate agnostic representation of the continuity and facilitates encoding of data where the independent variable may not be clear. For example total rainfall is dependent on time of day and how much rain has already fallen, and changing the coordinate system or time resolution should have no effect on how the records are connected to each other.

As with \autoref{eq:math:data:fiber:decompose} and \autoref{eq:math:data:monoid:decompose}, we can decompose the total space into component bundles $\pi:\dtotal_i\rightarrow \dbase$ where
\begin{equation}
    \label{eq:math:data:base:decompose}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
such that the monoid \(\monoid_{i}\) acts on component bundle \(\dtotal_i\). The \dbase\ remains the same because the continuity of the data does not change just because there are fewer components in each record.

@@

\subsubsection{Data Values}
\label{sec:math:data:section}
While the projection function $\pi:\dtotal \rightarrow\dbase$ ties together the base space \dbase\ with the fiber \dfiber, a section $\dsection: \dbase\rightarrow \dtotal$ encodes a dataset. A section function takes as input location $\dbasepoint \in \dbase$ and returns a record $\delement \in \dtotal$. For example, in the special case of a table \cite{spivakSIMPLICIALDATABASES}, \dbase\ is a set of row ids, \dfiber\ is the columns, and the section \dsection\ returns the record \delement\ at a given key in \dbase. For any fiber bundle, there exists a map
\begin{equation}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[d, "\pi"'] \\
                          & \dbase \arrow[u, "\dsection"', bend right]
    \end{tikzcd}
\end{equation}
 such that $\pi(\dsection(\dbasepoint)) = \dbasepoint$. The set of all global sections is denoted as $\Gamma(\dtotal)$. Assuming a trivial fiber bundle $\dtotal = \dbase \times \dfiber$, the section can be decomposed as 
\begin{equation}
    \label{eq:section_return}
    \dsection(\dbasepoint) = (\dbasepoint, (g_{\dfiber_{0}}(\dbasepoint), \ldots, g_{\dfiber_{n}}(\dbasepoint)))
\end{equation}
where $g: \dbase \rightarrow \dfiber$ is the index function into the fiber. This formulation of the section also holds on locally trivial sections of a non-trivial fiber bundle. Because we can decompose the bundle and the fiber (\autoref{eq:math:data:base:decompose}, \autoref{eq:math:data:fiber:decompose}), we can decompose \dsection\ as 
\begin{equation}
\label{eq:math:data:section:decompose}
\dsection= (\dsection_0,\ldots, \dsection_i, \dots, \dsection_n) 
\end{equation}
where each section $\dsection_i$ maps into a record on a component $\dfiber_i \in \dfiber$. This allows for accessing the data component wise in addition to accessing the data in terms of its location over \dbase.

\begin{figure}[H]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \caption{ Fiber (time, precipitation) with a 1D continuous \dbase\  defined on an interval $\left[0,n\right]$. The sections $\dsection^{(1)}$ and $\dsection^{(2)}$ are constrained such that the time variable must be monotonic, which means each section is a time series of precipitation values. They are included in the global set of sections  $\dsection^{(1)}, \dsection^{(2)} \in \Gamma(\dtotal)$}
    \label{fig:math:data:sections}
\end{figure}

In \autoref{fig:math:data:sections}, the fiber is the same encoding of $(time, \, precipitation)$ illustrated in \autoref{fig:math:data:fiber}, and the base space is the interval \dbase\ shown in \autoref{fig:math:data:base}. The section $\dsection^{(1)}$ is a function that for a point \dbasepoint\ returns a record in the fiber \dfiber. The section applied to a set of points in \dbase\ resolves to a series of monotonically increasing in time records of \textit{(time, precipitation)} values. Section $\dsection^{(2)}$ returns a different time series of \textit{(time, precipitation)} values. Both sections are included in the global set of sections $\dsection^{(1)}, \dsection^{(2)} \in \Gamma(\dtotal)$.

\subsubsection{Sheafs}
\label{sec:math:data:sheaf}
Dynamic visualizations require evaluating sections on different subspaces of \dbase; this can be achieved using a mathematical structure, called a sheaf $\mathcal{O}$, for defining collections of objects\cite{ghristElementaryAppliedTopology2014, ghristHomologicalAlgebraData2018,urbanikBriefIntroductionSchemes} on mathematical spaces.  On the fiber bundle \dtotal, we can describe a sheaf as the collection of local sections $\iota^{*}\dsection$
\begin{equation}
    \label{eq:sheaf}
    \begin{tikzcd}[column sep=huge]
        \iota^*\dtotal \arrow[d, "\pi"'] \arrow[r, "\iota^*", hook]             & \dtotal \arrow[d, "\pi"']                  \\
        U \arrow[r, "\iota", hook] \arrow[u, "\iota^{*}\dsection"', bend right] & \dbase \arrow[u, "\dsection"', bend right]
    \end{tikzcd}
\end{equation}
which are sections of \dtotal\ pulled back over local neighborhood $U \subset \dtotal$ via the inclusion map \(\iota:\dtotal\rightarrow U\). The collation of sections enabled by sheafs is necessary for navigation techniques such as pan and zoom\cite{NekrasovskiEvaluationPanZoom2006} and dynamically updated visualizations such as sliding windows\cite{crouchDynamicGraphsSlidingwindow2013,chuTimeSeriesSegmentation1995}.

\subsubsection{Applications}
Using fiber bundles as our data abstraction allows the model to be applicable to a wide variety of fields and use cases. For example, the section can be any instance of a numpy array\cite{harris2020array} that stores an image, such as an image where the \dbase\ is a 2D continuous plane and the \dfiber\ is $(\reals^{3}, \reals, \reals)$. In this fiber, the $\reals^3$ components encode color, and the other two components are the x and y positions of the sampled data in the image. The continuity of the image is implicitly encoded in the array as the index, so the position components encode the resolution. Instead of an image, the numpy array could also store a 2D discrete table. The fiber may not change, but the \dbase\ would now be 0D discrete points. These different choices in topology indicate, for example, what sorts of interpolation would be appropriate when visualizing the data. Labeled containers can also be described in this framework because of the schema like structure of the fiber. One such example is a pandas series which stores a labeled list, another is a  dataframe\cite{jeff_reback_2020_3715232} which has the structure of a relational table. A series could store the values of $\dsection^{(1)}$ and a second series could be  $\dsection^{(2)}$, while a dataframe would have multiple components and each data frame would be a unique section \dsection. The ability to encode complexity in continuity and components is particularly beneficial when working with  N dimensional labeled data containers. For example, an xarray\cite{hoyer2017xarray} data cube that stores precipitation would be a section of a fiber bundle with a \dbase\ that is a continuous volume and components \textit{(time, latitude, longitude, precipitation)}. This section does not need to resolve to values immediately and instead can be an instance of a distributed data container, such as a dask array \cite{rocklinDaskParallelComputation2015}. Our model provides a common formalism for describing widely used data containers without sacrificing the semantic structure embedded in each container.

>>>>

\section{Topological Equivariant Artist Model}
\label{sec:math}
To guide the implementation of structure preserving visualization components, we develop a mathematical formalism of visualization that specifies how these components preserve \textit{continuity} and \textit{equivariance}. Inspired by the analogous classes in Matplotlib\cite{hunterArchitectureOpenSource}, we call the transformation from data space to graphic space that these building block components implement the \textit{artist}.
\begin{equation}
    \label{eq:artist}
    \mathscr{\vartist}: \mathscr{\dtotal} \rightarrow \mathscr{\gtotal}
\end{equation}
The \textit{artist} \(\mathscr{\vartist}\) is a map from data \(\mathscr{\dtotal}\) to graphic \(\mathscr{\gtotal}\) fiber bundles. To explain how the \textit{artist} is a structure preserving map from data to graphic, we first model data (\autoref{sec:math:data}) and graphics (\autoref{sec:math:graphic}) as topological structures that encapsulate component types and continuity. We then discuss the functional maps from graphic to data (\autoref{sec:math:graphic:base}), data components to visual components (\autoref{sec:math:artist:nu}), and visual components into graphic (\autoref{sec:math:artist:q}) that make up the artist.

\subsection{Data Space \dtotal}
\label{sec:math:data}
We use fiber bundles as the data model because they are inclusive enough to express all the types of structures of data described in \autoref{sec:intro:data:tools}. A fiber bundle is a tuple \((\dtotal,\,\dbase,\,\pi ,\,\dfiber)\) defined by the projection map \(\pi\)
\begin{equation}
    \label{eq:fiber_bundle}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[r, "\pi"] & \dbase
    \end{tikzcd}
\end{equation}
that binds the components of the data in \dfiber\ to the continuity of the data encoded in \dbase. Our use of fiber bundles builds on Butler's work proposing that fiber bundles should be the common data abstraction for visualization data\cite{butlerVectorBundleClassesForm1992, butlerVisualizationModelBased1989}. The fiber bundle models the properties of data component types \dfiber\ (\autoref{sec:math:data:fiber}), the continuity of records \dbase\ (\autoref{sec:math:data:base}), the collections of records (\autoref{sec:math:data:section}), and the space \dtotal\ of all possible datasets with these components and continuity. By definition fiber bundles are locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}, meaning that over a localized neighborhood \(U\) the total space is the cartesian product \(\dbase\times\dfiber\).

\subsubsection{Variables in Fiber Space \dfiber}
\label{sec:math:data:fiber}
To formalize the structure of the data components, we use Spivak's description of the schema \cite{spivakSIMPLICIALDATABASES} as a fiber bundle to bind the components of the fiber to variable names and data types. Spivak constructs a set \ftotal\ that is the disjoint union of all possible objects of types \(\{\ftype_0, \ldots, \ftype_m\} \in \ftypes\), where \ftypes\ are the data types of the variables in the dataset. He then defines the single variable set \fttype\ 
\begin{equation}
    \label{eq:data_types}
    \begin{tikzcd}
        \fttype \arrow[r] \arrow[d, "\pi_{\fsection}"'] & \ftotal \arrow[d, "\pi"] \\
        \fnames \arrow[r, "\fsection"']                          & \ftypes       
    \end{tikzcd}
\end{equation}
which is \ftotal\ restricted to objects of type \ftype\ bound to variable name \fname. The \fttype\ lookup is by name to specify that every component is distinct, since multiple components can have the same type \ftype. Given \fsection, the fiber for a one variable dataset is
\begin{equation}
    \dfiber = \ftotal_{\fsection(\fname)} = \ftotal_{\ftype} 
\end{equation}
where \fsection\ is the schema that binds a variable name \fname\ to its datatype \ftype. A dataset with multiple components has a fiber that is the cartesian cross product of \(\ftotal_{\fsection}\) applied to all the columns:
\begin{equation}
F = \ftotal_{\fsection(\fname_{1})}\times \ldots \ftotal_{\fsection(\fname_{i})} \ldots\times \ftotal_{\fsection(\fname_{n})}
\end{equation}
which can also be written as 
\begin{equation}
    \label{eq:math:data:fiber:decompose}
    \dfiber= \dfiber_{0} \times \ldots \times \dfiber_{i}\times\ldots\times \dfiber_{n}
\end{equation}
which allows us to decouple \dfiber\ into components $\dfiber_i = \ftotal_{\fsection{(\fname_{i})}}$.

@@

The base space \dbase\ provides a way to explicitly encode the continuity of the data, as described in \autoref{sec:intro:data:continuity}. This explicit topology is a concise way of distinguishing between visualizations that appear identical but assume different continuity, for example heat maps and images. The base space \dbase\ acts as an indexing space, as emphasized by Butler\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}, to express how the records in \dtotal\ are connected to each other. As shown in \autoref{fig:math:data:base:types}, \dbase\ can have any number of dimensions and can be continuous or discrete. Formally \dbase\ is the quotient space \cite{QuotientSpaceTopology2020} of \dtotal\, meaning it is the finest space\cite{aurouxMath131Introduction} such that every \(\dbasepoint \in \dbase\) has a corresponding fiber \(\dfiber_k\)\cite{QuotientSpaceTopology2020}.

\begin{figure}[H]
    \includegraphics[width=\linewidth]{figures/math/k_qspace.png}
    \caption{The total space \dtotal\ is divided into fiber segments \dfiber. The base space \dbase\ acts as an index into the records in the fibers, such that every point \dbasepoint\ has a corresponding fiber \(\dfiber_{\dbasepoint}\). The projection map \(\pi\) maps every fiber \(\dfiber_{\dbasepoint}\) to a point \(\dbasepoint \in \dbase\) in the base space.}
    \label{fig:math:data:base:div}
\end{figure}

In \autoref{fig:math:data:base:div}, \dtotal\ is a rectangle divided by vertical fibers \dfiber, so the minimal \dbase\ for which there is always a mapping \(\pi: \dtotal\rightarrow \dbase\) is the closed interval \(\left[0,1\right]\). While the total space \dtotal\ may have components in \dfiber\ that describe any given point \(\dbasepoint \in \dbase\), such as \textit{time, latitude, longitude}, these labels are indexed into from \dbase\ the same as any other components. In contrast to the structural \textit{keys} with associated \textit{values} proposed by Munzner\cite{munznerVisualizationAnalysisDesign2014}, our model treats keys \dbasepoint\ as a pure reference to topology. Decoupling the keys from their semantics allows the components identifying the keys to be altered, which provides for a coordinate agnostic representation of the continuity and facilitates encoding of data where the independent variable may not be clear. For example total rainfall is dependent on time of day and how much rain has already fallen; therefore changing the coordinate system should have no effect on how the records are connected to each other, as illustrated in \autoref{fig:intro:equivariance} where precipitation in inches and millimeters yield equivalent line plots.

As with \autoref{eq:math:data:fiber:decompose} and \autoref{eq:math:data:monoid:decompose}, we can decompose the total space into component bundles \(\pi:\dtotal_i\rightarrow \dbase\) where
\begin{equation}
    \label{eq:math:data:base:decompose}
    \pi:\dtotal_1\oplus\ldots\oplus \dtotal_i \oplus\ldots \oplus \dtotal_n \rightarrow \dbase
\end{equation}
such that the monoid \(\monoid_{i}\) acts on component bundle \(\dtotal_i\). The \dbase\ remains the same because the continuity of the data does not change just because there are fewer components in each record.

@@

\subsubsection{Data Values}
\label{sec:math:data:section}
While the projection function \(\pi:\dtotal \rightarrow\dbase\) ties together the base space \dbase\ with the fiber \dfiber, a section \(\dsection: \dbase\rightarrow \dtotal\) encodes a dataset. A section function takes as input location \(\dbasepoint \in \dbase\) and returns a record \(\delement \in \dtotal\). For example, in the special case of a table \cite{spivakSIMPLICIALDATABASES}, \dbase\ is a set of row ids, \dfiber\ is the columns, and the section \dsection\ returns the record \delement\ at a given key in \dbase. For any fiber bundle, there exists a map
\begin{equation}
    \begin{tikzcd}
        \dfiber \arrow[r, hook] & \dtotal \arrow[d, "\pi"'] \\
                          & \dbase \arrow[u, "\dsection"', bend right]
    \end{tikzcd}
\end{equation}
 such that \(\pi(\dsection(\dbasepoint)) = \dbasepoint\). The set of all global sections is denoted as \(\Gamma(\dtotal)\). Assuming a trivial fiber bundle \(\dtotal = \dbase \times \dfiber\), the section can be decomposed as 
\begin{equation}
    \label{eq:section_return}
    \dsection(\dbasepoint) = (\dbasepoint, (g_{\dfiber_{0}}(\dbasepoint), \ldots, g_{\dfiber_{n}}(\dbasepoint)))
\end{equation}
where \(g: \dbase \rightarrow \dfiber\) is the index function into the fiber. This formulation of the section also holds on locally trivial sections of a non-trivial fiber bundle. Because we can decompose the bundle and the fiber (\autoref{eq:math:data:base:decompose}, \autoref{eq:math:data:fiber:decompose}), we can decompose \dsection\ as 
\begin{equation}
\label{eq:math:data:section:decompose}
\dsection= (\dsection_0,\ldots, \dsection_i, \dots, \dsection_n) 
\end{equation}
where each section \(\dsection_i\) maps into a record on a component \(\dfiber_i \in \dfiber\). This allows for accessing the data component wise in addition to accessing the data in terms of its location over \dbase.

\begin{figure}[H]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \caption{ Fiber (time, precipitation) with a 1D continuous \dbase\  defined on an interval \(\left[0,n\right]\). The sections \(\dsection^{(1)}\) and \(\dsection^{(2)}\) are constrained such that the time variable must be monotonic, which means each section is a time series of precipitation values. They are included in the global set of sections  \(\dsection^{(1)}, \dsection^{(2)} \in \Gamma(\dtotal)\)}
    \label{fig:math:data:sections}
\end{figure}

In \autoref{fig:math:data:sections}, the fiber is the same encoding of \((time, \, precipitation)\) illustrated in \autoref{fig:math:data:fiber}, and the base space is the interval \dbase\ shown in \autoref{fig:math:data:base}. The section \(\dsection^{(1)}\) is a function that for a point \dbasepoint\ returns a record in the fiber \dfiber. The section applied to a set of points in \dbase\ resolves to a series of monotonically increasing in time records of \textit{(time, precipitation)} values. Section \(\dsection^{(2)}\) returns a different time series of \textit{(time, precipitation)} values. Both sections are included in the global set of sections \(\dsection^{(1)}, \dsection^{(2)} \in \Gamma(\dtotal)\).

\subsubsection{Sheafs}
\label{sec:math:data:sheaf}
Dynamic visualizations require evaluating sections on different subspaces of \dbase; this can be achieved using a mathematical structure, called a sheaf \(\mathcal{O}\), for defining collections of objects\cite{ghristElementaryAppliedTopology2014, ghristHomologicalAlgebraData2018,urbanikBriefIntroductionSchemes} on mathematical spaces.  On the fiber bundle \dtotal, we can describe a sheaf as the collection of local sections \(\iota^{*}\dsection\)
\begin{equation}
    \label{eq:sheaf}
    \begin{tikzcd}[column sep=huge]
        \iota^*\dtotal \arrow[d, "\pi"'] \arrow[r, "\iota^*", hook]             & \dtotal \arrow[d, "\pi"']                  \\
        U \arrow[r, "\iota", hook] \arrow[u, "\iota^{*}\dsection"', bend right] & \dbase \arrow[u, "\dsection"', bend right]
    \end{tikzcd}
\end{equation}
which are sections of \dtotal\ pulled back over local neighborhood \(U \subset \dtotal\) via the inclusion map \(\iota:\dtotal\rightarrow U\). The collation of sections enabled by sheafs is necessary for navigation techniques such as pan and zoom\cite{NekrasovskiEvaluationPanZoom2006} and dynamically updated visualizations such as sliding windows\cite{crouchDynamicGraphsSlidingwindow2013,chuTimeSeriesSegmentation1995}.

\subsubsection{Applications}
Using fiber bundles as the data abstraction allows the model to describe widely used data containers without sacrificing the semantic structure embedded in each container. For example, the section can be any instance of a numpy array\cite{harris2020array} that stores an image, such as an image where the \dbase\ is a 2D continuous plane and the \dfiber\ is \((\reals^{3}, \reals, \reals)\). In this fiber, the \(\reals^3\) components encode color, and the other two components are the x and y positions of the sampled data in the image. The continuity of the image is implicitly encoded in the array as the index, so the position components encode the resolution. Instead of an image, the numpy array could also store a 2D discrete table. The fiber may not change, but the \dbase\ would now be 0D discrete points. These different choices in topology indicate, for example, what sorts of interpolation would be appropriate when visualizing the data. 
Labeled containers can also be described in this framework because of the schema like structure of the fiber. One such example is a pandas series which stores a labeled list, another is a  dataframe\cite{jeff_reback_2020_3715232} which has the structure of a relational table. A series could store the values of \(\dsection^{(1)}\) and a second series could be  \(\dsection^{(2)}\), while a dataframe would have multiple components and each data frame would be a unique section \dsection. The ability to encode complexity in continuity and components is particularly beneficial when working with  N dimensional labeled data containers. For example, an xarray\cite{hoyer2017xarray} data cube that stores precipitation would be a section of a fiber bundle with a \dbase\ that is a continuous volume and components \textit{(time, latitude, longitude, precipitation)}. This section does not need to resolve to values immediately and instead can be an instance of a distributed data container, such as a dask array \cite{rocklinDaskParallelComputation2015}.
